Regression for correlated variables : application in steel industry

### 2014-01-24 www/Rennes.tex
translate
git-svn-id: svn://svn.r-forge.r-project.org/svnroot/correg@276 edb9625f-4e0d-4859-8d74-9fd3b1da38cb

	On note $I_2^c=\{1,\dots,p\}\setminus I_2$
Le modèle génératif s'écrit alors :
\begin{eqnarray}
	Y_{|X,S}=Y_{|X}&=&XA+\varepsilon_Y= X^{I_2^c}A_{I_2^c}+X^{I_2}A_{I_2}+\varepsilon_Y \textrm{ with } \varepsilon_Y \sim \mathcal{N}(0,\sigma_Y^2) \label{MainR}\\
	\forall j \in I_2 : \  X^j_{|X^{I_1^j},S}&=&X^{I_1^j}B_{I_1^j}^j + \varepsilon_{j} \textrm{ with } \varepsilon_j \sim \mathcal{N}(0,\sigma_j^2) \label{SR}\\
    \forall j \notin I_2 : \ X^j &=& f(\theta_j) \textrm{ free law}	
\end{eqnarray}
Where $B_{I_1^j}^j$ is the $p_1^j$-sized vector of the coefficients of the subregression.

We note that (\ref{MainR}) and (\ref{SR}) also give :
\begin{eqnarray}
	Y&=&X^{I_2^c} (A_{I_2^c}+ \sum_{j \in I_2}B^{j}_{I_1}A_{j})+  \sum_{j \in I_2}\varepsilon_{j}A_{j}+\varepsilon_Y \\
					&=& X^{I_2^c}\tilde{A}_{I_2^c}+ \tilde{\varepsilon}=X\tilde{A}+ \tilde{\varepsilon}\label{Trueexpl} 			
\end{eqnarray}
\section{Estimateur}
	Classical methods like Ordinary Least Squares (OLS) estimate $Y|X$ and obtain (Maximum Likelihood Estimation): 
		\begin{equation}
			\hat A = (X'X)^{-1}X'Y \textrm{ (ill-conditoned matrix to inverse)}
		\end{equation}
		With following properties :
		\begin{eqnarray}
			E[\hat{A}|X]&=&A \\
			Var[\hat{A}|X]&=& \sigma_Y^2(X'X)^{-1}
		\end{eqnarray}				
		And when correlations are strong, the matrix to invert is ill-conditioned and the variance explodes.

>>>>

	On note $I_2^c=\{1,\dots,p\}\setminus I_2$
Le modèle génératif s'écrit alors :
\begin{eqnarray}
	Y_{|X,S}&=&XA+\varepsilon_Y= X^{I_2^c}A_{I_2^c}+X^{I_2}A_{I_2}+\varepsilon_Y \textrm{ avec } \varepsilon_Y \sim \mathcal{N}(0,\sigma_Y^2) \label{MainR}\\
	\forall j \in I_2 : \  X^j_{|X^{I_1^j},S}&=&X^{I_1^j}B_{I_1^j}^j + \varepsilon_{j} \textrm{ avec } \varepsilon_j \sim \mathcal{N}(0,\sigma_j^2) \label{SR}\\
    \forall j \notin I_2 : \ X^j &=& f(\theta_j) \textrm{ loi quelconque}	
\end{eqnarray}
Où $B_{I_1^j}^j$ est le vecteur de taille $p_1^j$ des coefficients de la sous-régression de $X^j$.

On remarque que (\ref{MainR}) et (\ref{SR}) impliquent :
\begin{eqnarray}
	Y&=&X^{I_2^c} (A_{I_2^c}+ \sum_{j \in I_2}B^{j}_{I_1}A_{j})+  \sum_{j \in I_2}\varepsilon_{j}A_{j}+\varepsilon_Y \\
					&=& X^{I_2^c}\tilde{A}_{I_2^c}+ \tilde{\varepsilon}=X\tilde{A}+ \tilde{\varepsilon}\label{Trueexpl} 			
\end{eqnarray}
\section{Estimateur}
	Classical methods like Ordinary Least Squares (OLS) estimate $Y|X$ and obtain (Maximum Likelihood Estimation): 
		\begin{equation}
			\hat A = (X'X)^{-1}X'Y \textrm{ (ill-conditoned matrix to inverse)}
		\end{equation}
		With following properties :
		\begin{eqnarray}
			E[\hat{A}|X]&=&A \\
			Var[\hat{A}|X]&=& \sigma_Y^2(X'X)^{-1}
		\end{eqnarray}				
		And when correlations are strong, the matrix to invert is ill-conditioned and the variance explodes.
